---
title: "Quick start"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick start}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(shinyuieditor)
```


The following will show you how to get up and running with the ui editor from scratch. 

If you prefer video format, here's an [in-depth walkthrough of using the ui editor to create and edit a new app](https://youtu.be/2Z0NfNLEJJQ).


## Pre-reqs

- `shinyuieditor` package installed. See the [installing section](../index.html#installing)
- Shiny app with ui built using `gridlayout::gridpage()` (more layout functions coming soon.) See the [`gridlayout` package](https://github.com/rstudio/gridlayout) for more info.



## Running

### New app

If you set the argument `app_loc` to a location that does not yet exist, the launcher will ask a few and setup a simple template app for you to use with building.

```r
shinyuieditor::launch_editor(app_loc = "new-app/")

#> No app was found at location /Users/me/new_app.
#> Would you like to start a new app from a template?
#> 1: yes
#> 2: no
#>
#> Selection: 1
#> Which starter template would you like to use? (Sorry, it's an easy choice currently.)
#> 1: geyser
#>
#> Selection: 1
#> => Starting Shiny preview app...
#> ...
```

_In the future more starting templates will be offered, however, currently only a simple grid-layout recreation of the classic "Geyser" app is available._

### Existing app

Assuming there's an existing app (either `app.R` or `ui.R` and `server.R`) in the folder `existing-app/` relative to your current working directly (`getwd()`), then you start the ui-editor on that app by running the following code and pasting the returned link into your web-browser.

```r
shinyuieditor::launch_editor(app_loc = "existing-app/")
#> Live editor running at http://localhost:44509/app
```

---

## Editing your app

Once you're in the editor, any changes you make will automatically be written to your app's UI and the changes can be seen in real-time with the "App Preview" window.

For more info on how to perform various tasks with the editor, see `vignette("how-to")`. 

## Saving/Closing editor

When you're done, simply close the browser window (or press {control/command}-c in the console) to stop the editor preview process in R. Since all changes are eagerly applied there's no need to save.


